Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-08-16 doc/report/msc-report.tex
report: new techniques section.

One new techniques which can be used for OLAP data warehouses include Google's
BigTable, which is a distributed column-oriented schema-less database.

Google's MapReduce is a new technique for distributed parallel computations.

>>>>

The OLAP field contains much research, for instance complete techniques such as
Dwarf \cite{dwarf}, which is an OLAP engine, the Stanford Data Warehousing
Project \cite{thestanford}, and DROLAP \cite{drolap}.

Google is the originator of two recent techniques: BigTable---a distributed
column-oriented schema-less database---and MapReduce---a framework for
distributed parallel computations.

The following sections will present and review these two techniques.
